---
title: "Weight of Fish"
author: "Dominic Garibay"
date: "`Fall 2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```


```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch
```{r}
Perch.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

Perch.Summary <- summary(Perch.out)
as.data.frame(Perch.Summary$outmat)
subsets(Perch.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
### Best Models

Best Single Model - Height + Width

### Best Two regressor model

Best Double Model - Height + Width

## Pike

```{r}
Pike.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,      
               nvmax = NULL,   
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

Pike.Summary <- summary(Pike.out)
as.data.frame(Pike.Summary$outmat)
subsets(Pike.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

Best Model - Complete Model (L1+L2+L3+H+L)

### Best Two regressor model

Best Two Regressor Model L1-L3

## Roach

```{r}
Roach.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

Roach.Summary <- summary(Roach.out)
as.data.frame(Roach.Summary$outmat)
subsets(Roach.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

Best Model - Width + Length Three

### Best Two regressor model

Best Two Regression Model - Length 3 + Width

## Final Summary Statements

Only for Pike did the two element model not represent the best overall model for prediction of weight. Both the Perch and Roach had a two element model as their best predictor of weight. However the prediction models for Roach weight were significantly less accurate on average based on their adjusted r-squared values compared to those of the models of the other two fish species.
